\section{Devices}

\subsection{Yolo:bit}

\begin{itemize}
    \item \textbf{Application}: The Yolo:bit can be used as the central processing unit for controlling various smart home devices. It can handle input from sensors and output control signals to actuators.
    \item \textbf{Input}: It receives data from connected sensors like temperature, humidity, and light sensors.
    \item \textbf{Output}: It sends control signals to other components, such as the relay switch or servo motors, based on the inputs it receives.
\end{itemize}

\subsection{Expansion Board}

\begin{itemize}
    \item \textbf{Application}: This board allows for the connection of multiple sensors and devices to the Yolo:bit.
    \item \textbf{Input}: It receives signals from various connected sensors.
    \item \textbf{Output}: It sends signals to the Yolo:bit, allowing it to process the information and control other devices.
\end{itemize}

\subsection{Temperature and Humidity Sensor DHT20}

\begin{itemize}
    \item \textbf{Application}: Monitors the temperature and humidity levels in the environment.
    \item \textbf{Input}: The sensor continuously collects temperature and humidity data from the environment.
    \item \textbf{Output}: It sends the temperature and humidity data to the Yolo:bit for processing.
\end{itemize}

\subsection{Light Sensor}

\begin{itemize}
    \item \textbf{Application}: Used to monitor the ambient light levels in the room.
    \item \textbf{Input}: It measures the intensity of light in the environment.
    \item \textbf{Output}: The sensor sends the light intensity data to the Yolo:bit for further processing.
\end{itemize}

\subsection{Distance Sensor}

\begin{itemize}
    \item \textbf{Application}: Used for security, this sensor detects the presence of people or objects by measuring distance. It can be used for detecting intruders or monitoring door openings.
    \item \textbf{Input}: It sends distance measurements to the Yolo:bit, which can determine whether there is movement or an obstacle in the monitored area.
    \item \textbf{Output}: The sensor’s output is a distance value that can be used to trigger alerts or security systems.
\end{itemize}
    
\subsection{Servo Motor}

\begin{itemize}
    \item \textbf{Application}: Used to control doors. The servo motor allows precise positioning, which is essential for tasks like opening or closing a door.
    \item \textbf{Input}: The servo receives a signal from the Yolo:bit to determine its position.
    \item \textbf{Output}: The servo moves to a specific position, such as opening or closing a door.
\end{itemize}
    
\subsection{Mini Fan}

\begin{itemize}
    \item \textbf{Application}: A fan can be controlled to adjust the airflow and cool the room.
    \item \textbf{Input}: The fan receives a signal from the Yolo:bit.
    \item \textbf{Output}: It provides airflow by turning on or off, depending on the control signal it receives.
\end{itemize}

\subsection{LED RGB Lights}

\begin{itemize}
    \item \textbf{Application}: The LED RGB lights can be controlled to change colors and brightness, creating different lighting effects or ambiance in the room.
    \item \textbf{Input}: The lights receive control signals from the Yolo:bit based on data from sensors or user preferences.
    \item \textbf{Output}: The lights change their color and brightness according to the signals received, providing desired lighting effects.
\end{itemize}

 

